Heat transport in stratified convection across mach number blahdy blah

### 2016-08-11 tex/nusselt_paper.tex
small updates -- gets some first refs in

%\documentclass[iop]{emulateapj}
\documentclass[aps, prl, twocolumn, groupedaddress]{revtex4-1}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{color}
\usepackage{bm}
\usepackage{empheq}
\usepackage{natbib}
\usepackage{cancel}
\usepackage[colorlinks=True, linkcolor=blue]{hyperref}
\usepackage[all]{hypcap}

\bibliographystyle{apj}

@@

%%%%% Body of the paper
\section{Introduction \label{section:intro}}
Blah Blah stuff.

@@

We use initial conditions of randomized temperature perturbations on the order of $10^{-6}$ below the background
temperature field (EVAN -- TRY TO DO 1E-6*EPSILON).

>>>>

%\documentclass[iop]{emulateapj}
\documentclass[aps, prl, twocolumn, groupedaddress]{revtex4-1}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{color}
\usepackage{bm}
\usepackage{empheq}
\usepackage{natbib}
\usepackage{cancel}
\usepackage[colorlinks=True, linkcolor=blue, citecolor=blue]{hyperref}
\usepackage[all]{hypcap}

\bibliographystyle{apsrev}

@@

%%%%% Body of the paper
\section{Introduction \label{section:intro}}
Talk about \cite{hurlburt&all1984, brummell&all1996, cattaneo&all1991},  and then talk about some
\RB stuff, such as \cite{johnston&doering2009}.

@@

We use initial conditions of randomized temperature perturbations on the order of $10^{-6}$ below the background
temperature field (EVAN -- TRY TO DO 1E-6*EPSILON). We impose stress free, impenetrable, constant temperature boundary
conditions.
